Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-08 README.Rmd
format change

- information about the files in the repository,
- instructions for knitting the paper,
- descriptions of the bullet data used in the paper, 
- information on the font sizes used for the figures in the manuscript, 
- and the steps taken to create the `submission` folder.

### Description of Items in Repository

@@

### Instructions for Knitting Paper

@@

### Additional Information on Bullet Data

@@

### Figure Font Size Information

@@

### Steps Followed to Create the Submission Folder

>>>>

- information about the files in the repository,
- instructions for knitting the paper,
- descriptions of the bullet data used in the paper, 
- information on the font sizes used for the figures in the manuscript, and
- the steps taken to create the `submission` folder.

## Description of Items in Repository

@@

## Instructions for Knitting Paper

@@

## Additional Information on Bullet Data

@@

## Figure Font Size Information

@@

## Steps Followed to Create the Submission Folder
